Abstract Plots

### 2022-08-10 paper_analysis.Rmd
Changes to figures including combined effect of FFPE percent and cosine similarity. Cleanup of previous markdowns and files

# When is `excerno` a good classifier?

We hypothesize that the performance of our classifier depends on how different the base mutational signature is from the FFPE signature.

@@

A straightforward way of calculating the similarity across signatures the cosine similarity. So we first generate the cosine similarity of all the COSMIC signatures against the FFPE signature:

@@

And we try `test_mix_mutations` and plot the results to check it is working:

@@

We create a function that calculates the average metrics over a fixed number of simulations `num_iter` and test it

@@

  1:num_iter %>% 
    map_dfr(~calc_metrics_mix(cosmic_idx,num_cosmic,num_ffpe))  %>%
    pivot_longer(1:3) %>% 
    group_by(name) %>%
    summarize(mean = mean(value)) %>%
    mutate(sbs = baseline_name)
}

calc_metrics_mix_num(1,10,500,500)
calc_metrics_mix_num(4,10,500,500)
calc_metrics_mix_num(6,10,500,500)
```

## Simulations across all COSMIC signatures

@@

First we summarize the metrics across all the COSMIC mutational signatures

@@

ggsave("paper_figures/supp2.png", dpi = 300, width = 175, height = 75, units = "mm")

@@

## Performance characteristics vs similarity against FFPE signature

Now we explore the relationship of the performance metrics against the similarity between the baseline signature and FFPE using a figure

@@

We define a function to represent the mutational signatures that fall below a threshold for a particular metric.

@@

  ggplot(new_tbl, aes(x = ffpe_cos, y = mean))+
    geom_point()+
    geom_smooth(method = "lm", se=FALSE)+
    geom_point(data = fixed_below, color = "red")+
    geom_point(data = fixed_above, color = "deepskyblue")+
    geom_hline(yintercept=threshold, linetype="dashed", color = "red")+
    geom_label_repel(data=fixed_below, aes(label=sbs))+
    geom_label_repel(data=fixed_above, aes(label=sbs))+
    labs(x = "Cosine similarity against FFPE signature", 
         y="")+
    facet_wrap(.~name, strip.position="left")+
    theme(strip.text.y = element_text(size = 15),
          axis.title.x = element_text (size=15))
}
```

@@

And we create auxiliar function for getting the coefficients of the linear model and their fit

@@

# What is the influence of FFPE percentage in the performance of `excerno`?

@@

So we will mimick our original scenario scenario of SBS4 and SBS6, however this time we will introduce varying proportions going from 5% to 100% every 5%.

@@

ggplot(sbs6_dilution_tbl, 
       aes(x=pct_ffpe, y=mean)) +
  geom_point()+
  geom_smooth(se=FALSE)+
  facet_grid(name~.) + 
  geom_hline(yintercept=0.8, linetype="dashed",color = "red")

@@

Let's combine both datasets in a single graph, coloring by signature

@@

dilution_tbl %>%
  filter(name != "Accuracy") %>%
  ggplot(aes(x=pct_ffpe, y=mean, color=sbs)) +
    geom_point()+
    geom_smooth(se=FALSE,formula=y~x, method=loess)+
    facet_wrap(.~name, strip.position="left")+
    geom_hline(yintercept=0.8, linetype="dashed",color = "red")+
    labs(x= "Percent of FFPE signature",
         y="",
         color = "Signature")+
    scale_x_continuous(breaks = scale_x, labels = scale_x)+
    scale_y_continuous(breaks = scale_y, labels = scale_y)+
    theme(strip.text.y = element_text(size = 15),
          axis.title.x = element_text (size=15))

@@

## A general approach

@@

Now we are ready to calculate the dillution metrics across all COSMIC mutational signatures (this takes 20min to run)

```{r}
set.seed(123456)
# Full dataset run
sim_dillution_tbl <- 1:sbs_num %>%
  map_dfr(~calc_dillution_metrics(pct_ffpe, .x))

rep_ffpe_cos <- rep(ffpe_cosmic_cos_sims, each=length(pct_ffpe)*3)

@@

sim_dillution_tbl %>%
  filter (metric!="Accuracy") %>%
  ggplot (aes(x=pct_ffpe, y=mean)) +
    geom_smooth(se=FALSE, method="loess", formula="y~x", size=.75)+
    geom_point (alpha=0.2) +
    facet_wrap(.~metric, strip.position="left")+
    geom_hline(yintercept=0.8, linetype="dashed",color = "red", size=0.5)+
    scale_x_continuous(breaks = scale_x, labels = scale_x)+
    scale_y_continuous(breaks = scale_y, labels = scale_y)+
    labs(x= "Percent of FFPE signature",
         y="")+
    theme(strip.text.y = element_text(size = 15),
          axis.title.x = element_text (size=15))

@@

We are interested in plotting the performance characteristics across multiple dillution levels so we define a function to do that:

@@

  ggplot(new_tbl, aes(x = ffpe_cos, y = mean))+
    geom_point()+
    geom_smooth(method = "lm", se=FALSE, formula="y~x")+
    geom_hline(yintercept=threshold, linetype="dashed", color = "red")+
    geom_point(data = fixed_below, color = "red")+
    geom_point(data = fixed_above, color = "deepskyblue")+
    geom_label_repel(data=fixed_below, aes(label=sbs))+
    geom_label_repel(data=fixed_above, aes(label=sbs))+
    facet_grid(pct_ffpe~metric, labeller=labeller(pct_ffpe=grid.labs))+
    labs(x = "Cosine similarity against FFPE signature", 
         y = "")+
    theme(strip.text.x = element_text(size = 15),
          strip.text.y = element_text(size = 12),
          axis.title.x = element_text (size=15))
}
```

```{r}
perf_grid = c(10,30,50,70,90)
plot_metrics_grid_excerno(sim_dillution_tbl, perf_grid, 
                          fixed_sbs, c("Sensitivity","Specificity"),0.8)
ggsave("paper_figures/fig3b.png", dpi = 300, width = 150, height = 150, units = "mm")
```

@@

Here is the information for each of the performance characteristics:

@@

@@

## Another way to look at it (Omit)

We know that

* Sensitivity is a decreasing function of percent FFPE.
* Specificity is an increasing function of percent FFPE.

We would like to summarize this characteristics more succintly and establish the relationship with the similarity against the FFPE signature. To do that we will we fix a threshold value in 80% and:

* We will record the maximum ffpe where sensitivity drops below this threshold. We will call this **maximum permissible sensitivy FFPE* 
* We will record the first percent ffpe where specificity rises above this threshold **minimum permissible specificity FFPE*

```{r}
threshold <- 0.8

sens_thres_tbl <- sim_dillution_tbl %>%
  filter (metric == "Sensitivity") %>%
  filter(mean>threshold) %>%
  group_by (sbs) %>%
  slice (which.max(pct_ffpe)) %>%
  ungroup() %>%
  mutate(cos = ffpe_cosmic_cos_sims)

spec_thres_tbl <- sim_dillution_tbl %>%
  filter (metric == "Specificity" ) %>%
  filter (mean > threshold) %>%
  group_by (sbs) %>%
  slice (which.min(pct_ffpe)) %>%
  ungroup() %>%
  mutate(cos = ffpe_cosmic_cos_sims)
```

Let's look at the distribution of those thresholds

```{r}
sens_thres_tbl %>%
  summarize (median = median (mean),
           IQR = IQR(mean)) %>%
  mutate_if(is.numeric, format, digits=2) %>%
  kbl() %>%
  kable_styling()

spec_thres_tbl %>%
  summarize (median = median (mean),
           IQR = IQR(mean)) %>%
  mutate_if(is.numeric, format, digits=2) %>%
  kbl() %>%
  kable_styling()

ggplot(sens_thres_tbl, aes(x=pct_ffpe))+
  geom_histogram(binwidth=5, color="black", fill="lightblue")+
  labs(x= "Percent of FFPE signature",
       y="Number")

ggplot(spec_thres_tbl, aes(x=pct_ffpe))+
  geom_histogram(binwidth=5, color="black", fill="lightblue")+
  labs(x= "Percent of FFPE signature",
       y="Number")

And let's plot the relationship with similarity against the FFPE signature:

```{r}
sens_thres_tbl %>%
  ggplot (aes(cos, pct_ffpe)) +
  geom_point() + 
  geom_smooth(method="lm", formula = "y~x")+
  scale_x_continuous(breaks = scale_y, labels = scale_y)+
  scale_y_continuous(breaks = scale_x, labels = scale_x)+
  labs(x= "Cosine similarity against FFPE",
         y="Extreme percent FFPE")

spec_thres_tbl %>%
  ggplot (aes(cos, pct_ffpe)) +
  geom_point() + 
  geom_smooth(method="lm", formula = "y~x")+
  scale_x_continuous(breaks = scale_y, labels = scale_y)+
  scale_y_continuous(breaks = scale_x, labels = scale_x)+
  labs(x= "Cosine similarity against FFPE",
         y="Extreme percent FFPE")

And the linear model metrics for each case:

```{r}
sens_thres_lm <- lm (pct_ffpe ~ cos, sens_thres_tbl)

spec_thres_lm <- lm (pct_ffpe ~ cos, spec_thres_tbl)

summary(sens_thres_lm)
summary(spec_thres_lm)
```

>>>>

# The effect of mutational signatures in `excerno`

We hypothesize that the performance of our classifier depends on how the similarity of the base mutational signature against the FFPE signature.

@@

A straightforward way of calculating the similarity across signatures is the cosine similarity. So we first generate the cosine similarity of all the COSMIC signatures against the FFPE signature:

@@

We try `test_mix_mutations` and plot the results to check it is working:

@@

Finally we create a function `calc_metrics_mix_num` that calculates the average metrics across a fixed number of simulations `num_iter`

@@

  1:num_iter %>% 
    map_dfr(~calc_metrics_mix(cosmic_idx,num_cosmic,num_ffpe))  %>%
    pivot_longer(1:3) %>% 
    group_by(name) %>%
    summarize(mean = mean(value)) %>%
    mutate(sbs = baseline_name)
}
```

And we test it using our to-go signatures `SBS1`, `SBS4`, and `SBS6`

```{r}
calc_metrics_mix_num(1,10,500,500)
calc_metrics_mix_num(4,10,500,500)
calc_metrics_mix_num(6,10,500,500)
```

## Testing across all COSMIC signatures

@@

We summarize the performance metrics across all the COSMIC mutational signatures

@@

@@

## Performance metrics vs similarity against FFPE signature

Now we explore the relationship of the performance metrics against the similarity between the baseline signature and FFPE :

@@

To a varying extent it seems there is a linear trend across all the mutational signatures.

Now we define a function that polishes the previous graph and plots two signatures on it (`SBS4` and `SBS6`). The two fixed signatues will have different shape and color depending on whether or not they meet a threshold of 80%

@@

  ggplot(new_tbl, aes(x = ffpe_cos, y = mean))+
    geom_point()+
    geom_smooth(method = "lm", se=FALSE)+
    geom_point(data = fixed_below, fill = "red", shape=24, size=3)+
    geom_point(data = fixed_above, fill = "blue",shape=22, size=3)+
    geom_hline(yintercept=threshold, linetype="dashed", color = "red")+
    geom_label_repel(data=fixed_below, aes(label=sbs))+
    geom_label_repel(data=fixed_above, aes(label=sbs))+
    labs(x = "Cosine similarity against FFPE signature", 
         y="")+
    facet_wrap(.~name, strip.position="left")+
    theme(strip.text.y = element_text(size = 15),
          axis.title.x = element_text (size=15))
}
```

@@

And we create a function for getting the coefficients of the linear model and their fit

@@

# The effect of FFPE percent in the performance of `excerno`.

@@

So we will mimic our original scenario scenario of `SBS4` and `SBS6`, however this time we will introduce varying proportions going from 10% to 90% every 5%.

@@

ggplot(sbs6_dilution_tbl, 
       aes(x=pct_ffpe, y=mean)) +
  geom_point()+
  geom_smooth(se=FALSE, method="loess", formula=y~x)+
  facet_grid(name~.) + 
  geom_hline(yintercept=0.8, linetype="dashed",color = "red")

@@

Let's combine both datasets in a single graph, focusing on sensitivity and specificity and coloring by signature

@@

dilution_tbl %>%
  filter(name != "Accuracy") %>%
  ggplot(aes(x=pct_ffpe, y=mean, color=sbs, shape=sbs)) +
    geom_point()+
    geom_smooth(se=FALSE,formula=y~x, method=loess)+
    facet_wrap(.~name, strip.position="left")+
    geom_hline(yintercept=0.8, linetype="dashed",color = "red")+
    labs(x= "Percent of FFPE signature",
         y="",
         color = "Signature",
         shape="")+
    scale_x_continuous(breaks = scale_x, labels = scale_x)+
    scale_y_continuous(breaks = scale_y, labels = scale_y)+
    theme(strip.text.y = element_text(size = 15),
          axis.title.x = element_text (size=15))+
    guides(shape= "none")

@@

## Simulating across all COSMIC signatures

@@

Now we are ready to calculate the dilution metrics across all COSMIC mutational signatures (this takes 20min to run)

```{r}
set.seed(123456)
# sbs_num <- 3
# Full dataset run
sim_dillution_tbl <- 1:sbs_num %>%
  map_dfr(~calc_dillution_metrics(pct_ffpe, .x))

rep_ffpe_cos <- rep(ffpe_cosmic_cos_sims[1:sbs_num], each=length(pct_ffpe)*3)

@@

sim_dillution_tbl %>%
  filter (metric!="Accuracy") %>%
  ggplot (aes(x=pct_ffpe, y=mean)) +
    geom_smooth(se=FALSE, method="loess", formula="y~x", size=.75)+
    geom_point (alpha=0.2) +
    facet_wrap(.~metric, strip.position="left")+
    geom_hline(yintercept=0.8, linetype="dashed",color = "red", size=0.5)+
    scale_x_continuous(breaks = scale_x, labels = scale_x)+
    scale_y_continuous(breaks = scale_y, labels = scale_y)+
    labs(x= "Percent of FFPE signature",
         y="")+
    theme(strip.text.y = element_text(size = 15),
          axis.title.x = element_text (size = 15))

@@

We are interested in plotting the performance characteristics across multiple dilution levels so we define a function to do that:

@@

  ggplot(new_tbl, aes(x = ffpe_cos, y = mean))+
    geom_point()+
    geom_smooth(method = "lm", se=FALSE, formula="y~x")+
    geom_hline(yintercept=threshold, linetype="dashed", color = "red")+
    geom_point(data = fixed_below, fill = "red", shape=24, size=3)+
    geom_point(data = fixed_above, fill = "blue",shape=22, size=3)+
    geom_label_repel(data=fixed_below, aes(label=sbs))+
    geom_label_repel(data=fixed_above, aes(label=sbs))+
    facet_grid(pct_ffpe~metric, labeller=labeller(pct_ffpe=grid.labs))+
    labs(x = "Cosine similarity against FFPE signature", 
         y = "")+
    theme(strip.text.x = element_text(size = 15),
          strip.text.y = element_text(size = 12),
          axis.title.x = element_text (size=15))
}
```

```{r}

perf_grid = c(10,30,50,70,90)
fixed_sbs = c("SBS4", "SBS6")
plot_metrics_grid_excerno(sim_dillution_tbl, perf_grid, 
                          fixed_sbs, c("Sensitivity","Specificity"),0.8)
ggsave("paper_figures/fig3b.png", dpi = 300, width = 150, height = 150, units = "mm")
```

@@

Finally we make sure that the ffpe content is on the decimal scale (to be consistent) with the cosine similarity, which is a number from 0 to 1.

@@

Here is the information of the models for sensitivity and specificity

@@

# Conclusion

We tested our method across varying levels of FFPE content and across different mutational signatures. We found that the performance characteristics of our method decrease as the cosine similarity against the FFPE signature increases. We also establish that FFPE content increases, our sensitivity decreases and our specificity increases and establish linear models with good fit.

This analysis was done using the following environment:

### 2022-08-10 sandbox/Abstract.Rmd
Changes to figures including combined effect of FFPE percent and cosine similarity. Cleanup of previous markdowns and files

# Scatterplot of Average AUC vs. Cosine Similarity to FFPE

```{r, include=FALSE}
set.seed(500)
#outer for loop: loop through each COSMIC v3 signature
average.auc.values <- c()
for (x in 1:length(signature.names)){
  signature.auc.vec <- c()
  #inner for loop: calculate misclassification rate 10x for each signature
  for (y in 1:10){
    #create a sample vector of 100 mutations for the COSMIC signature corresponding to number x
    sample.vec <- create_signature_sample_vector(signature.matrix.list[[x]],500)
    #Create FFPE sample vector of 100 mutations
    ffpe.sample.vec <- create_signature_sample_vector(ffpe.signature, 500)
    classification.df.1 <- 
      get_classification_df(list(sample.vec, ffpe.sample.vec), 
                            c(signature.names[x],"FFPE"), 
                            list(signature.matrix.list[[x]], ffpe.signature))

    class.df.colnames <- colnames(classification.df.1)
    sig.name <- class.df.colnames[3]
    classification.df.2 <- classification.df.1 %>%
      mutate(signature.indicator = ifelse(truth == sig.name, 1, 0))
    predictions <- classification.df.2[3]
    labels <- classification.df.2$signature.indicator
    pred <- prediction(predictions, labels)
    auc.perf <- performance(pred, measure = "auc")
    signature.auc.vec[y] <- auc.perf@y.values[[1]][1]
  }
  average.signature.auc <- mean(signature.auc.vec)
  average.auc.values[x] <- average.signature.auc
}
```

```{r, include=FALSE}
cos.sim.auc.data <- data.frame(signature.names, ffpe.cosmic.cos.sims, average.auc.values)
colnames(cos.sim.auc.data) <- c("signature", "cosine_similarity", "average_auc")
```

```{r, include=FALSE}

ggplot(cos.sim.auc.data, aes(x=average_auc)) +
  geom_histogram(color="black", fill="lightblue")+
  labs( x = "Average AUC", y = "Count")
#ggsave("supp.fig.5.png", dpi = 300, width = 175, height = 108, units = "mm")

median(cos.sim.auc.data$average_auc)
IQR(cos.sim.auc.data$average_auc)

model2 <- lm(average_auc ~ cosine_similarity, data = cos.sim.auc.data)

model2_summary <- summary(model2)

cos.sim.auc.data$residuals <- model2_summary$residuals

cos.sim.auc.outliers <- cos.sim.auc.data %>%
  filter(average_auc<0.8)

cos.sim.auc.outliers

cos.sim.auc.outliers2 <- cos.sim.auc.data %>%
  filter(average_auc>=0.8 & average_auc<0.9)

cos.sim.sbs4 <- cos.sim.auc.data %>%
  filter(signature=="SBS4")

```{r, include=FALSE}
ggplot(cos.sim.auc.data, aes(x = cosine_similarity, y = average_auc))+
  geom_point()+
  geom_smooth(method = "lm", se=FALSE)+
  labs( x = "Cosine similarity between baseline COSMIC and FFPE signatures", y = "Average AUC")+
  geom_point(data = cos.sim.auc.outliers, color = "red")+
  geom_point(data = cos.sim.auc.outliers2, color = "purple")+
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  geom_hline(yintercept=0.9, linetype="dashed", color = "purple")+
  geom_label_repel(data = cos.sim.auc.outliers, aes(label = signature), max.overlaps = 10, label.size =   0.1)+
  geom_label_repel(data = cos.sim.auc.outliers2, aes(label = signature), max.overlaps = 10, label.size =   0.1)+
  geom_label_repel(data = cos.sim.sbs4, aes(label = signature), max.overlaps = 10, label.size =   0.1)

#ggsave("Fig2b.png", dpi = 300, width = 175, height = 108, units = "mm")

# Scatterplot of Average Sensitivity and Specificity vs. Cosine Similarity to FFPE

```{r, include=FALSE}
set.seed(500)
#outer for loop: loop through each COSMIC v3 signature
average.sensitivity.values <- c()
average.specificity.values <- c()
for (x in 1:length(signature.names)){
  signature.sensitivity.vec <- c()
  signature.specificity.vec <- c()
  #inner for loop: calculate misclassification rate 10x for each signature
  for (y in 1:10){
    #create a sample vector of 100 mutations for the COSMIC signature corresponding to number x
    sample.vec <- create_signature_sample_vector(signature.matrix.list[[x]],100)
    #Create FFPE sample vector of 100 mutations
    ffpe.sample.vec <- create_signature_sample_vector(ffpe.signature, 100)
    classification.df <- get_classification_df(list(sample.vec, ffpe.sample.vec), c(signature.names[x],"FFPE"), list(signature.matrix.list[[x]], ffpe.signature))
    class.df.colnames <- colnames(classification.df)
    sig.name <- class.df.colnames[3]
    #Count number of true positives (for sensititivity)
    sensitivity.df <- classification.df %>%
      filter(truth == sig.name & classify == sig.name)
    #Calculate sensitivity
    sensitivity.val = nrow(sensitivity.df)/100
    #Add to the vector of 10 sensitivity values
    signature.sensitivity.vec[y] = sensitivity.val
    #Count number of true negatives (for specificity)
    specificity.df <- classification.df %>%
      filter(truth == "FFPE" & classify == "FFPE")
    #Calculate specificity
    specificity.val = nrow(specificity.df)/100
    #Add to the vector of 10 specificity values
    signature.specificity.vec[y] = specificity.val
  }
  average.signature.sensitivity <- mean(signature.sensitivity.vec)
  average.sensitivity.values[x] <- average.signature.sensitivity
  average.signature.specificity <- mean(signature.specificity.vec)
  average.specificity.values[x] <- average.signature.specificity
}
```

```{r, include=FALSE}
sens.spec.data <- data.frame(signature.names, ffpe.cosmic.cos.sims, average.sensitivity.values, average.specificity.values)

colnames(sens.spec.data) <- c("signature", "cosine_similarity", "sensitivity", "specificity")

ggplot(sens.spec.data, aes(x=sensitivity)) +
  geom_histogram(color="black", fill="lightblue")+
  labs( x = "Average sensitivity", y = "Count")
#ggsave("supp.fig.3.png", dpi = 300, width = 175, height = 108, units = "mm")

median(sens.spec.data$sensitivity)
IQR(sens.spec.data$sensitivity)

outliers <- sens.spec.data %>%
  filter(sensitivity<0.8 | signature=="SBS4" | signature=="SBS6")

ref.signatures <- sens.spec.data %>%
  filter(signature=="SBS4" )

ggplot(sens.spec.data, aes(x = cosine_similarity, y = sensitivity))+
  geom_point()+
  geom_smooth(method = "lm", se=FALSE)+
  labs( x = "Cosine similarity between baseline COSMIC and FFPE signatures", y = "Average sensitivity")+
  geom_point(data = outliers, color = "red")+
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  geom_label_repel(data = outliers, aes(label = signature), max.overlaps = 10, label.size =   0.1)

#ggsave("supp.fig6.png", dpi = 300, width = 175, height = 108, units = "mm")

model.sens <- lm(sensitivity ~ cosine_similarity, data = sens.spec.data)

summary(model.sens)

ggplot(sens.spec.data, aes(x=specificity)) +
  geom_histogram(color="black", fill="lightblue")+
  labs( x = "Average specificity", y = "Count")
#ggsave("supp.fig.4.png", dpi = 300, width = 175, height = 108, units = "mm")

median(sens.spec.data$specificity)
IQR(sens.spec.data$specificity)

outliers <- sens.spec.data %>%
  filter(specificity<0.8 | signature=="SBS4" | signature=="SBS6")

ggplot(sens.spec.data, aes(x = cosine_similarity, y = specificity))+
  geom_point()+
  geom_smooth(method = "lm", se=FALSE)+
  labs( x = "Cosine similarity between baseline COSMIC and FFPE signatures", y = "Average specificity")+
  geom_point(data = outliers, color = "red")+
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  geom_label_repel(data = outliers, aes(label = signature), max.overlaps = 10, label.size =   0.1)

#ggsave("supp.fig7.png", dpi = 300, width = 175, height = 108, units = "mm")

model.spec <- lm(specificity ~ cosine_similarity, data = sens.spec.data)

summary(model.spec)

@@

```{r}
cosmic.sig4 = signature.matrix.list[[4]]
cosmic.sig6 = signature.matrix.list[[6]]
ffpe.sig = ffpe.signature
```

@@

<!-- # Mutational load performance characteristics -->

<!-- ## Mutational load predictions -->

<!-- ```{r} -->

<!-- step_load = seq(50, 1000, by = 50) -->

<!-- MMR.probabilities <- vector(mode = "list", length = length(step)) -->

<!-- MMR.truth <- vector(mode = "list", length = length(step)) -->

<!-- for (x in 1:length(step)){ -->

<!--   sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2) -->

<!--   ffpe.truth <- rep("FFPE", step[x]/2) -->

<!--   sample.sig6 <- create_signature_sample_vector(cosmic.sig6, step[x]/2) -->

<!--   sig6.truth <- rep("MMR", step[x]/2) -->

<!--   test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"), -->

<!--                                 list(cosmic.sig6, ffpe.sig)) -->

<!--   classification <- test %>% -->

<!--     mutate(trueBinary = ifelse(truth == "MMR",1,0)) -->

<!--   MMR.probabilities[[x]] <- classification$MMR -->

<!--   MMR.truth[[x]] <- classification$trueBinary -->

<!-- } -->

<!-- ``` -->

<!-- ```{r} -->

<!-- tob.probabilities <- vector(mode = "list", length = length(step)) -->

<!-- tob.truth <- vector(mode = "list", length = length(step)) -->

<!-- for (x in 1:length(step)){ -->

<!--   sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2) -->

<!--   ffpe.truth <- rep("FFPE", step[x]/2) -->

<!--   sample.sig4 <- create_signature_sample_vector(cosmic.sig4, step[x]/2) -->

<!--   sig4.truth <- rep("tob", step[x]/2) -->

<!--   test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"), -->

<!--                                 list(cosmic.sig4, ffpe.sig)) -->

<!--   classification <- test %>% -->

<!--     mutate(trueBinary = ifelse(truth == "Tobacco",1,0)) -->

<!--   tob.probabilities[[x]] <- classification$Tobacco -->

<!--   tob.truth[[x]] <- classification$trueBinary -->

<!-- } -->

<!-- ``` -->

<!-- ```{r} -->

<!-- load.MMR <- prediction(MMR.probabilities, MMR.truth) -->

<!-- load.tob <- prediction(tob.probabilities, tob.truth) -->

<!-- ``` -->

<!-- ## Sensitivity -->

<!-- ```{r} -->

<!-- load.sens.MMR.vec = evaluate_perf(100, length(step_load), load.MMR, "sens") -->

<!-- load.sens.tob.vec = evaluate_perf(100, length(step_load), load.tob, "sens") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #plot(step, load.sens.MMR.vec, ylim = c(0,1)) -->

<!-- sensitivity = append(load.sens.MMR.vec, load.sens.tob.vec) -->

<!-- signature.sens = append(rep("MMR", length(load.sens.MMR.vec)), -->

<!--                         rep("Tobacco", length(load.sens.tob.vec))) -->

<!-- dilution = append(step, step) -->

<!-- sens.df <- data.frame(dilution, sensitivity, signature.sens) -->

<!-- ggplot(data = sens.df, mapping = aes(x = dilution,  -->

<!--                                      y = sensitivity,  -->

<!--                                      color = signature.sens)) + -->

<!--   geom_point() + -->

<!--   geom_smooth() + -->

<!--   labs(title = "Sensitivity as a function of mutational load", -->

<!--        x = "Number of mutations in each sample", -->

<!--        y = "Sensitivity value", -->

<!--        color = "True signal") + -->

<!--   coord_cartesian(ylim = c(0,1)) -->

<!-- ``` -->

<!-- ## Specificity -->

<!-- ```{r} -->

<!-- load.spec.MMR.vec = evaluate_perf(100, length(step.load), load.MMR, "spec") -->

<!-- load.spec.tob.vec = evaluate_perf(100, length(step.load), load.tob, "spec") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #plot(step, load.spec.MMR.vec, ylim = c(0,1)) -->

<!-- specificity = append(load.spec.MMR.vec, load.spec.tob.vec) -->

<!-- signature.spec = append(rep("MMR", length(load.spec.MMR.vec)), -->

<!--                         rep("Tobacco", length(load.spec.tob.vec))) -->

<!-- dilution = append(step, step) -->

<!-- spec.df <- data.frame(dilution, specificity, signature.spec) -->

<!-- ggplot(data = spec.df, mapping = aes(x = dilution,  -->

<!--                                      y = specificity,  -->

<!--                                      color = signature.spec)) + -->

<!--   geom_point() + -->

<!--   geom_smooth() + -->

<!--   labs(title = "Specificity as a function of mutational load", -->

<!--        x = "Number of mutations in each sample", -->

<!--        y = "Specificity value", -->

<!--        color = "True signal") + -->

<!--   coord_cartesian(ylim = c(0,1)) -->

<!-- ``` -->

>>>>

@@

```{r}
cosmic.sig4 = signature_matrix_list[[4]]
cosmic.sig6 = signature_matrix_list[[6]]
ffpe.sig = ffpe_signature
```

@@
